Galaxy Zoo: Morphological Classifications for 120,000 Galaxies in HST Legacy Imaging

### 2016-09-07 response.md

We have added text to explicitly mark the difference between the two equations in what is now Section 4.2.

-----------------------------------
Minor Comment 4
-----------------------------------

***4) I probably should have mentioned this above, but why are the authors not working with equation (4) as the basis of their regression model?***

Equation 2 was originally left unbounded because the raw data being fit was inherently bounded between vote fractions of 0 and 1. However, the original verseion of Equation 4 could produce vote fractions greater than 1 if left in the same form as Equation 2. We have realized that the difference in normalization, while having only a small effect on the fitting of the data, is inconsistent and may be confusing to a reader. Therefore, we have changed Equation 2 to match Equation 4 (see response to Major Comment II, as well as Minor Comment 3). All data in the tables and catalog have been updated to account for these small changes.

### 2016-09-07 writeup/gz_hubble_data_draft_2.tex
Mark the change in Fig 11 caption (MiC 5). See #181.

\begin{figure}
\center
\includegraphics[width=0.5\textwidth]{figures/zeta_mu.pdf}
\caption{All fits for the \ferengi{} galaxies of the vote fraction dropoff
parameter $\zeta$ for \ffeatures{} as a function of surface brightness. This
includes only galaxies with a bounded range on the dropoff
($-10<\zeta<10$) and sufficient points to fit each function (37~original
galaxies, each artificially redshifted in eight bins over a range from $0.3\lesssim z_\mathrm{sim}\lesssim1.0$).}
\label{fig:zeta_mu}
\end{figure}

>>>>

\begin{figure}
\center
\includegraphics[width=0.5\textwidth]{figures/zeta_mu.pdf}
\caption{All fits for the \ferengi{} galaxies of the vote fraction dropoff
parameter $\zeta$ for \ffeatures{} as a function of surface brightness. This
includes only galaxies with a bounded range on the dropoff
\changes{($-10<\zeta<10$)} and sufficient points to fit each function (37~original
galaxies, each artificially redshifted in eight bins over a range from $0.3\lesssim z_\mathrm{sim}\lesssim1.0$).}
\label{fig:zeta_mu}
\end{figure}
